---
title: "Tool Use Analysis"
author: "Jonathan Pertile"
format: pdf
editor: visual
---

```{r}
#load packages
library(tidyverse)
library(tidymodels)
library(knitr)
library(ape)
library(caper)
library(phytools)
library(nlme)
library(gee)
library(TreeTools)
library(patchwork)
library(phylolm)
library(broom)
library(readxl)

#load data and phylogenetic tree
tool_use_expanded <- read_xlsx("PrimateToolUseDataset.xlsx", sheet = "Dataset")
tooluse.tree <- read.nexus("ToolUsePhylo54.nex")
```



```{r}
#this ensures that phylogeny and data have species in the same order
species <- tibble(TipLabels(tooluse.tree, single = TRUE)) |> 
  rename("Species" = 1)

tool_use_expanded2 <- merge(species, tool_use_expanded, sort = FALSE)

#this turns dummy variables into factors
tool_use_expanded2$Omnivore <- as.factor(tool_use_expanded2$Omnivore)
tool_use_expanded2$Folivore <- as.factor(tool_use_expanded2$Folivore)
tool_use_expanded2$Frugivore <- as.factor(tool_use_expanded2$Frugivore)
```

```{r}
row.names(tool_use_expanded2) <- tool_use_expanded2$Species
rownames(tool_use_expanded2) == tooluse.tree$tip.label
#row names in the database matchup with tree tip labels ??
```


```{r}
#this is the global model with all variables included
set.seed(1)
model <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached 
         log.alpha.bound = 8) #increased so alpha doesn't reach bound
```

#WARNING: the following code chunks will take a long time to run

There are 63 different ways to include 6 different variables in the model.

```{r}
#modelito means little model 
#modelitos do not include all the variables
#there are 63 ways to choose which variables to include/exclude
#so there are 63 modelitos

#excluding 1 variable

modelito101 <- phyloglm(Tool_Use ~
               log(Group_Size, 2) + Omnivore + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito102 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                Omnivore + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito103 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito104 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito105 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito106 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito107 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito108 <- phyloglm(Tool_Use ~
              Omnivore + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito109 <- phyloglm(Tool_Use ~
                Omnivore + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito110 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito111 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito112 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito113 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito114 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               + Omnivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito115 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               + Omnivore + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito116 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               + Omnivore + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito117 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito118 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito119 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito120 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito121 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito122 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2) + Omnivore + Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito123 <- phyloglm(Tool_Use ~ Folivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound
         
modelito124 <- phyloglm(Tool_Use ~ Omnivore + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound
         
modelito125 <- phyloglm(Tool_Use ~ Omnivore + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito126 <- phyloglm(Tool_Use ~ Omnivore + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito127 <- phyloglm(Tool_Use ~
               log(Group_Size, 2) + Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito128 <- phyloglm(Tool_Use ~
               log(Group_Size, 2) + Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito129 <- phyloglm(Tool_Use ~
               log(Group_Size, 2) + Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito130 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito131 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito132 <- phyloglm(Tool_Use ~ 
               log(Group_Size, 2) + Omnivore + Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito133 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Frugivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito134 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Folivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito135 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Folivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito136 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Omnivore + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito137 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Omnivore + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito138 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
                 Omnivore + Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito139 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2)  + Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito140 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2)  + Omnivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito141 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2)  + Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito142 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2)  + Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito143 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               log(Group_Size, 2),
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito144 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               Omnivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito145 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito146 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito147 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2) +
               Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito148 <- phyloglm(Tool_Use ~ log(Group_Size, 2) +
               Omnivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito149 <- phyloglm(Tool_Use ~ log(Group_Size, 2) +
               Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito150 <- phyloglm(Tool_Use ~ log(Group_Size, 2) +
               Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito151 <- phyloglm(Tool_Use ~ log(Group_Size, 2) +
               Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito152 <- phyloglm(Tool_Use ~ Omnivore +
               Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito153 <- phyloglm(Tool_Use ~ Omnivore +
               Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito154 <- phyloglm(Tool_Use ~ Omnivore +
               Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito155 <- phyloglm(Tool_Use ~ Folivore +
               Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito156 <- phyloglm(Tool_Use ~ Dexterity_Index +
               Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito157 <- phyloglm(Tool_Use ~ Frugivore +
               Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito158 <- phyloglm(Tool_Use ~ log(Brain_Weight_grams, 2),
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito159 <- phyloglm(Tool_Use ~ log(Group_Size, 2),
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito160 <- phyloglm(Tool_Use ~ Omnivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito161 <- phyloglm(Tool_Use ~ Folivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito162 <- phyloglm(Tool_Use ~ Frugivore,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound

modelito163 <- phyloglm(Tool_Use ~ Dexterity_Index,
         data = tool_use_expanded2, 
         phy = tooluse.tree, 
         method = c("logistic_IG10"),
         btol = 20, #the limit had been reached somewhere
         log.alpha.bound = 8) #increased so alpha doesn't reach bound
```

```{r}
a <- rbind(modelito101$aic) |> rbind(modelito102$aic) |> rbind(modelito103$aic) |> rbind(modelito104$aic) |> rbind(modelito105$aic) |> rbind(modelito106$aic) |> rbind(modelito107$aic) |> rbind(modelito108$aic) |> rbind(modelito109$aic) |> rbind(modelito110$aic) |> rbind(modelito111$aic) |> rbind(modelito112$aic) |> rbind(modelito113$aic) |> rbind(modelito114$aic) |> rbind(modelito115$aic) |> rbind(modelito116$aic) |> rbind(modelito117$aic) |> rbind(modelito118$aic) |> rbind(modelito119$aic) |> rbind(modelito120$aic) |> rbind(modelito121$aic) |> rbind(modelito122$aic) |> rbind(modelito123$aic) |> rbind(modelito124$aic) |> rbind(modelito125$aic) |> rbind(modelito126$aic) |> rbind(modelito127$aic) |> rbind(modelito128$aic) |> rbind(modelito129$aic) |> rbind(modelito130$aic) |> rbind(modelito131$aic) |> rbind(modelito132$aic) |> rbind(modelito133$aic) |> rbind(modelito134$aic) |> rbind(modelito135$aic) |> rbind(modelito136$aic) |> rbind(modelito137$aic) |> rbind(modelito138$aic) |> rbind(modelito139$aic) |> rbind(modelito140$aic) |> rbind(modelito141$aic) |> rbind(modelito142$aic) |> rbind(modelito143$aic) |> rbind(modelito144$aic) |> rbind(modelito145$aic) |> rbind(modelito146$aic) |> rbind(modelito147$aic) |> rbind(modelito148$aic) |> rbind(modelito149$aic) |> rbind(modelito150$aic) |> rbind(modelito151$aic) |> rbind(modelito152$aic) |> rbind(modelito153$aic) |> rbind(modelito154$aic) |> rbind(modelito155$aic) |> rbind(modelito156$aic) |> rbind(modelito157$aic) |> rbind(modelito158$aic) |> rbind(modelito159$aic) |> rbind(modelito160$aic) |> rbind(modelito161$aic) |> rbind(modelito162$aic) |> rbind(modelito163$aic) 

min(a)
a

```


```{r}
#modelito 145 has the lowest AIC, so it is selected and presented
set.seed(1)
summary(modelito145)
```

Interpreting results:
```{r}
logodds_BW <- 0.59631
odds_BW <- exp(logodds_BW)


logodds_FO <- -1.61035
odds_FO <- exp(logodds_FO)

odds_BW
odds_FO
```

Holding all other variables constant, we expect that, on average, every doubling in brain mass increases the odds of observed tool use behavior by a factor of 1.82. 

Holding all other variables constant, we expect that, on average, the odds of observed tool use behavior in folivores is lower than in other primates by a factor of 0.200. 

